Illusion Game Validation (part 2)

### 2022-12-30 study3/study3.Rmd
added labels to y-axis in fig 3

---
title: "Illusion Game Validation (part 2)"
author: "Dominique Makowski et al."
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: paper
    code_folding: hide
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
bibliography: "../submission/references.bib"
---

@@

```{r demographics}
p_age <- estimate_density(dfsub$Age) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(fill = "#607D8B") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age", color = NULL) +
  theme_modern() +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    plot.subtitle = element_text(face = "italic", hjust = 0.5),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank()
  )

p_nat <- dfsub |>
  group_by(Nationality) |>
  summarize(n = n()) |>
  mutate(Nationality = fct_reorder(Nationality, desc(n))) |>
  ggplot(aes(x = Nationality, y = n, fill = Nationality)) +
  geom_bar(stat = "identity") +
  labs(y = "Number", title = "Nationality") +
  scale_fill_material_d(guide = "none") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_modern() +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    plot.subtitle = element_text(face = "italic", hjust = 0.5),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_text(size = rel(0.8)),
    axis.text.x = element_text(size = rel(0.6), angle = 50, hjust = 1)
  )

# ggsave("figures/figure_dem1.png",
#        patchwork::wrap_elements(p_age / p_nat),
#        width=0.5*(fig.height),
#        height=1*(fig.height), dpi=1000, bg="white")

@@

# ggsave("figures/figure_dem2.png",
#        patchwork::wrap_elements(p_sex / p_edu / p_race), width=1*(fig.height), height=1*(fig.height), dpi=1000, bg="white")

p_ipip <- dfsub |>
  select(starts_with("IPIP") & !ends_with("_SD")) |>
  estimate_density() |>
  mutate(
    Parameter = str_remove_all(Parameter, "IPIP6_"),
    Parameter = str_replace(Parameter, "HonestyHumility", "Honesty-Humility")
  ) |>
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line(size = 1) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = c("Agreeableness" = "#FFC107", "Honesty-Humility" = "#00BCD4", "Extraversion" = "#9C27B0", "Conscientiousness" = "#3F51B5", "Openness" = "#4CAF50", "Neuroticism" = "#E91E63")) +
  labs(x = "Score", title = "Normal Personality", color = NULL) +
  theme_modern() +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank(),
    legend.text = element_text(size = rel(0.8))
  )

p_pid <- dfsub |>
  select(starts_with("PID") & !ends_with("_SD")) |>
  estimate_density() |>
  mutate(
    Parameter = str_remove_all(Parameter, "PID5_"),
    Parameter = str_replace(Parameter, "NegativeAffect", "Negative Affect")
  ) |>
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line(size = 1) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = c("Antagonism" = "#FF9800", "Detachment" = "#03A9F4", "Disinhibition" = "#FF5722", "Negative Affect" = "#F44336", "Psychoticism" = "#673AB7")) +
  labs(x = "Score", title = "Pathological Personality", color = NULL) +
  theme_modern() +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank(),
    legend.text = element_text(size = rel(0.8))
    # legend.position = "top",
  )

# ggsave("figures/figure_dem3.png",
#        patchwork::wrap_elements(p_ipip / p_pid), width=2/3*(fig.height), height=1*(fig.height), dpi=1000, bg="white")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p <- patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_dem.png"), interpolate = TRUE)) /
  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_agesex.png"), interpolate = TRUE)) /
  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_pers.png"), interpolate = TRUE)) +
  plot_layout(heights = c(7200, 5000, 8000))

ggsave("../figures/figure3.png", p, height = 20200, width = 15166, units = "px", limitsize = FALSE)
```

>>>>

---
title: "Illusion Game Validation (part 2)"
author: "Dominique Makowski et al."
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: paper
    code_folding: hide
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
bibliography: "../submission/R1/references.bib"
---

@@

```{r demographics}
p_age <- estimate_density(dfsub$Age) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(fill = "#607D8B") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = expression("Age"[" (in years)"]), color = NULL, y = "Distribution") +
  theme_modern(axis.title.space = 5) +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    plot.subtitle = element_text(face = "italic", hjust = 0.5),
    axis.title.y = element_text(size = rel(0.8)),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank()
  )

p_nat <- dfsub |>
  group_by(Nationality) |>
  summarize(n = n()) |>
  mutate(Nationality = fct_reorder(Nationality, desc(n))) |>
  ggplot(aes(x = Nationality, y = n, fill = Nationality)) +
  geom_bar(stat = "identity") +
  labs(y = "Number of participants", title = "Nationality") +
  scale_fill_material_d(guide = "none") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme_modern(axis.title.space = 5) +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    plot.subtitle = element_text(face = "italic", hjust = 0.5),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = rel(0.8)),
    axis.text.y = element_text(size = rel(0.8)),
    axis.text.x = element_text(size = rel(0.6), angle = 50, hjust = 1)
  )

ggsave("figures/figure_dem1.png",
       patchwork::wrap_elements(p_age / p_nat),
       width=0.5*(fig.height),
       height=1*(fig.height), dpi=1000, bg="white")

@@

ggsave("figures/figure_dem2.png",
       patchwork::wrap_elements(p_sex / p_edu / p_race), width=1*(fig.height), height=1*(fig.height), dpi=1000, bg="white")

p_ipip <- dfsub |>
  select(starts_with("IPIP") & !ends_with("_SD")) |>
  estimate_density() |>
  mutate(
    Parameter = str_remove_all(Parameter, "IPIP6_"),
    Parameter = str_replace(Parameter, "HonestyHumility", "Honesty-Humility")
  ) |>
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line(size = 1) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = c("Agreeableness" = "#FFC107", "Honesty-Humility" = "#00BCD4", "Extraversion" = "#9C27B0", "Conscientiousness" = "#3F51B5", "Openness" = "#4CAF50", "Neuroticism" = "#E91E63")) +
  labs(x = "Score", title = "Normal Personality", y = "Distribution", color = NULL) +
  theme_modern(axis.title.space = 5) +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    axis.text.y = element_blank(),
    axis.title.y = element_text(size = rel(0.8)),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank(),
    legend.text = element_text(size = rel(0.8))
  )

p_pid <- dfsub |>
  select(starts_with("PID") & !ends_with("_SD")) |>
  estimate_density() |>
  mutate(
    Parameter = str_remove_all(Parameter, "PID5_"),
    Parameter = str_replace(Parameter, "NegativeAffect", "Negative Affect")
  ) |>
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line(size = 1) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = c("Antagonism" = "#FF9800", "Detachment" = "#03A9F4", "Disinhibition" = "#FF5722", "Negative Affect" = "#F44336", "Psychoticism" = "#673AB7")) +
  labs(x = "Score", title = "Pathological Personality", y = "Distribution", color = NULL) +
  theme_modern(axis.title.space = 5) +
  theme(
    plot.title = element_text(size = rel(1), face = "bold", hjust = 0.5),
    axis.text.y = element_blank(),
    axis.title.y = element_text(size = rel(0.8)),
    axis.text.x = element_text(size = rel(0.8)),
    axis.title.x = element_blank(),
    legend.text = element_text(size = rel(0.8))
    # legend.position = "top",
  )

ggsave("figures/figure_dem3.png",
       patchwork::wrap_elements(p_ipip / p_pid), width=2/3*(fig.height), height=1*(fig.height), dpi=1000, bg="white")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p <- 
  # patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_dem.png"), interpolate = TRUE)) /
  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_agesex.png"), interpolate = TRUE)) /
  patchwork::wrap_elements(grid::rasterGrob(png::readPNG("figures/figure_pers.png"), interpolate = TRUE)) +
  # plot_layout(heights = c(7200, 5000, 8000))
  plot_layout(heights = c(5000, 8000))

ggsave("../figures/figure4.png", p, height = 5000+8000, width = 15166, units = "px", limitsize = FALSE)
```
